---
title: "SI-Quant_FullAnalysis"
author: "Rose Schneider"
date: "11/14/2016"
output: html_document
---

Full and updated analysis for Horowitz, Schneider, & Frank (under review). Codebase is being updated to streamline and consolidate in advance of and prep for submission. All updated code is validated against the original output.

#Preliminaries
```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
opts_chunk$set(cache=FALSE, message=FALSE, warning=FALSE, error=FALSE)  
```

```{r}
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(stringr)
library(tidyr)
library(markdown)
library(directlabels)
library(magrittr)
library(bootstrap)
library(langcog)
library(diptest)
library(lme4)
theme_set(theme_bw())

setwd("~/Documents/Projects/si_paper/analyses/analysis/")
```

#Experiment 1

##Data management
```{r}
d <- read.csv("../data/implicatures_adhocScalar_data.csv")

#fill in the selection types for easier analyses
d_exp1=melt.data.frame(d,c("Subj_ID", "age","agegroup", "gender"),c("carrots", "hats", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", 
"carrots_condition", "hats_condition", "cookies_condition", "trains_condition", "cats_condition", "purses_condition",  "keys_condition", "shirts_condition", "breads_condition", "horses_condition", "bears_condition", "frogs_condition", "plates_condition", "books_condition", "elephants_condition", "lamps_condition", "bananas_condition", "butterflies_condition", 
"carrots_type", "hats_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))

data_exp1 <- d_exp1[1:864,] 
data_exp1$condition <- d_exp1$value[865:1728]
data_exp1$type <- d_exp1$value[1729:2592]
names(data_exp1)[5] <- "item"
names(data_exp1)[6] <- "correct"

#some tidying
data_exp1 %<>%
  mutate(trial_type = ifelse(type == "implicature", "Implicature", "Control")) %>%
  mutate(type = factor(type, levels = c("implicature","control_comparison","control_distractor",
					      "control_none","control_unambiguous", "control_all"), 
				    	  labels = c("Implicature","Comparison","Distractor","None","Unambig. Some", "All")),
         condition = factor(condition, levels = c("adhoc", "scalar"), 
                            labels = c("Ad hoc", "Scalar")))

```         
    
##Demographic information          
```{r}
exp1_demo <- data_exp1 %>%
  distinct(agegroup, Subj_ID, gender, age)%>%
  group_by(agegroup) %>%
  summarise(n = n(), 
            n_female = sum(gender == "f"), 
            n_male = sum(gender == "m"), 
            mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age))
```

##Mean performance across conditions, by agegroup
```{r}
ms_exp1 <- data_exp1 %>%
  mutate(correct = as.numeric(correct))%>%
  group_by(condition, type, trial_type, agegroup)%>%
  multi_boot_standard("correct", na.rm = TRUE)

pdf(file="./exp1_performance.pdf", width=6.5, height=4)
p <- ggplot(data = ms_exp1,aes(x=type, y=mean, fill=type, alpha=agegroup)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  geom_linerange(aes(ymin = ci_lower,
                      ymax = ci_upper),
                  size = .3,
                  show.legend = FALSE,
                 position=position_dodge(width = 0.9)) +
  theme_bw(base_size = 10) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_alpha_manual(values=c(0.8, 1), 
                     guide = guide_legend(title = "Age group (years)")) + 
  labs(x = "Trial Type", y = "Mean Correct") +
  scale_fill_solarized() +
facet_grid(~condition, scale = "free_x") + guides(fill = FALSE)
print(p)
aux <- dev.off()
```

###T-tests of performance across trial types and age groups

```{r}
d <- data_exp1 %>%
  filter(condition == "Scalar")%>%
  mutate(correct = as.numeric(correct))

d <- aggregate(correct ~ type + agegroup +  Subj_ID, data=d, mean)
```


###T-tests: Age-groups, by trial type
```{r}
#t-tests against "all"
#4-4.5
#all-some
t.test(subset(d, agegroup == "4.0--4.5" & type == "All")$correct,
       subset(d, agegroup == "4.0--4.5" & type == "Implicature")$correct,
       var.equal = TRUE)
#all-none
t.test(subset(d, agegroup == "4.0--4.5" & type == "All")$correct,
       subset(d, agegroup == "4.0--4.5" & type == "None")$correct,
       var.equal = TRUE)
#all-unambig.some
t.test(subset(d, agegroup == "4.0--4.5" & type == "All")$correct,
       subset(d, agegroup == "4.0--4.5" & type == "Unambig. Some")$correct,
       var.equal = TRUE)

#4.5-5
#all-some
t.test(subset(d, agegroup == "4.5--5.0" & type == "All")$correct,
       subset(d, agegroup == "4.5--5.0" & type == "Implicature")$correct,
       var.equal = TRUE)
#all-none
t.test(subset(d, agegroup == "4.5--5.0" & type == "All")$correct,
       subset(d, agegroup == "4.5--5.0" & type == "None")$correct,
       var.equal = TRUE)
#all-unambig.some
t.test(subset(d, agegroup == "4.5--5.0" & type == "All")$correct,
       subset(d, agegroup == "4.5--5.0" & type == "Unambig. Some")$correct,
       var.equal = TRUE)

#SI between ages
t.test(subset(d, agegroup == "4.5--5.0" & type == "Implicature")$correct,
       subset(d, agegroup == "4.5--5.0" & type == "Implicature")$correct,
       var.equal = TRUE)
```

###T-tests: Scalar vs. ad hoc
T-tests: Scalar vs. ad-hoc
```{r}
d1 <- data_exp1 %>%
  mutate(correct = as.numeric(correct))

d1 <- aggregate(correct ~ type + agegroup + condition + Subj_ID, data=d1, mean)

#comparison - ad-hoc implicature vs. scalar
#4-4.5
t.test(subset(d1, agegroup == "4.0--4.5" & type == "Implicature" 
              & condition == "Ad hoc")$correct,
       subset(d1, agegroup == "4.0--4.5" & type == "Implicature" 
              & condition == "Scalar")$correct,
       var.equal = TRUE)

#4.5-5
t.test(subset(d1, agegroup == "4.5--5.0" & type == "Implicature" 
              & condition == "Ad hoc")$correct,
       subset(d1, agegroup == "4.5--5.0" & type == "Implicature" 
              & condition == "Scalar")$correct,
       var.equal = TRUE)
```

###Diptest for bimodal performance
```{r}
ms1 <- data_exp1 %>%
  group_by(type, condition, Subj_ID) %>%
  mutate(correct = as.numeric(correct)) %>%
  summarise(mean = mean(correct), 
            agegroup = agegroup[1]) %>%
  filter(condition == "Scalar")

cs <- cast(ms1, Subj_ID + agegroup ~ type + condition, value="mean") %>%
  rename(control_none_scalar = None_Scalar, 
         implicature_scalar = Implicature_Scalar, control_all_scalar = All_Scalar)

dip.test(cs$implicature_scalar)
dip.test(cs$control_none_scalar)
dip.test(cs$control_all_scalar)
```

####Graph of bimodal distribution
```{r}
exp1_hist <- data_exp1 %>%
  filter(condition == "Scalar" & type != "All" & type != "Unambig. Some")%>%
  group_by(Subj_ID, type)%>%
  mutate(correct = as.numeric(correct))%>%
  multi_boot_standard("correct", na.rm = TRUE)

pdf(file="./exp1_hist.pdf", width=6, height=3.5)
q <- ggplot(exp1_hist, aes(x = mean, fill=type)) + 
  geom_histogram(colour = "black", stat = "bin",breaks = c(0,.2,.4,.6,.8,1), binwidth = .2) + 
  theme_bw(base_size = 18) + 
  xlab("Mean performance") + 
  ylab("Frequency") + 
  facet_wrap(~type) + 
  theme_bw(base_size = 10) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        legend.position = "none") +
  scale_fill_solarized() + 
  scale_x_continuous(breaks = c(0,.2,.4,.6,.8,1))
print(q)
aux <- dev.off()
```

###Full correlations
```{r}
#full correlations
cor.test(cs$control_none_scalar, cs$implicature_scalar)
cor.test(cs$control_all_scalar, cs$implicature_scalar)
cor.test(cs$control_none_scalar, cs$control_all_scalar)

#by age
#none-some
cs %>% group_by(agegroup) %>% 
	summarise(r = cor.test(control_none_scalar, implicature_scalar)$estimate,
			  p = cor.test(control_none_scalar, implicature_scalar)$p.value)
#all-some
cor.test(cs$control_all_scalar, cs$implicature_scalar)
cs %>% group_by(agegroup) %>% 
	summarise(r = cor.test(control_all_scalar, implicature_scalar)$estimate,
			  p = cor.test(control_all_scalar, implicature_scalar)$p.value)
#all-none
cor.test(cs$control_all_scalar, cs$control_none_scalar)
cs %>% group_by(agegroup) %>% 
	summarise(r = cor.test(control_all_scalar, control_none_scalar)$estimate,
			  p = cor.test(control_all_scalar, control_none_scalar)$p.value)	
```
  
###Logistic regression
```{r}
#center age to facilitate model fit
data_exp1 %<>%
  mutate(age.c = as.vector(scale(age, center = TRUE, scale=FALSE)))%>%
  mutate(correct = as.integer(correct))

gl <- glmer(correct ~ trial_type * condition * age.c  + 
              (trial_type | Subj_ID), data=data_exp1, 
            family=binomial, control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))) 

lm <- glmer(correct ~ trial_type * condition * age.c +
              (trial_type| Subj_ID) + (trial_type|item), 
            data = data_exp1, family = binomial, control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
#change optimizer, otherwise model won't converge
summary(lm)
summary(gl)
```
  
#Experiment 2

##Read in data
```{r}
d2 <- read.csv("../data/implicatures_scalarOnly_data.csv")

data_exp2=melt.data.frame(d2,c("Subj_ID","age","agegroup","gender", "ethnicity"),c("carrots", "hats", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", 
"carrots_selectionType", "hats_selectionType", "cookies_selectionType", "trains_selectionType", "cats_selectionType", "purses_selectionType",  "keys_selectionType", "shirts_selectionType", "breads_selectionType", "horses_selectionType", "bears_selectionType", "frogs_selectionType", "plates_selectionType", "books_selectionType", "elephants_selectionType", "lamps_selectionType", "bananas_selectionType", "butterflies_selectionType", 
"carrots_type", "hats_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))

data <- data_exp2[1:918,] 
data$selectionType <- data_exp2$value[919:1836]
data$type <- data_exp2$value[1837:2754]
names(data)[4] <- "gender"
names(data)[5] <-"ethnicity"
names(data)[6] <- "item"
names(data)[7] <- "correct"

data_exp2 <- data

data_exp2 %<>%
  mutate(type = factor(type, levels = c("all","some","none"), 
				    	  labels = c("All","Some","None")),
         selectionType = factor(selectionType, levels = c("all", "some", "none"), 
                            labels = c("All", "Some", "None")), 
         correct = as.numeric(correct))

attach(data_exp2)
data_exp2$trial_type[type == "some"] <- "implicature"
data_exp2$trial_type[type != "some"] <- "control"
detach(data_exp2)

```

###Demographic information
```{r}
demo_exp2 <- data_exp2 %>%
  distinct(agegroup, age, gender, ethnicity, Subj_ID)%>%
  group_by(agegroup)%>%
  summarise(n = n(), 
            n_female = sum(gender == "f"), 
            n_male = sum(gender == "m"), 
            mean_age = mean(age), 
            median_age = median(age), 
            sd_age = sd(age), 
            n_white = sum(ethnicity == "white"), 
            n_asian = sum(ethnicity == "asian"), 
            n_black = sum(ethnicity == " black"), 
            n_other = sum(ethnicity == "mixed" | ethnicity == "other"), 
            n_na = sum(is.na(ethnicity)))

```

##Mean performance by trial and age group
```{r}
ms_exp2 <- data_exp2 %>%
  group_by(type, agegroup)%>%
  multi_boot_standard("correct", na.rm=T)

pdf(file="./exp2_performance.pdf", width=6, height=3.5)
p <- 
quartz()
ggplot(data = ms_exp2, aes(x=type, y=mean, fill=type, alpha=agegroup)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  geom_linerange(aes(ymin = ci_lower,
                      ymax = ci_upper),
                  size = .3,
                  show.legend = FALSE,
                 position=position_dodge(width = 0.9)) +
  theme_bw(base_size = 10) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_alpha_manual(values=c(0.5,.625, .725, 1), 
                     guide = guide_legend(title = "Age group (years)")) + 
  labs(x = "Trial Type", y = "Mean Correct") +
  scale_fill_solarized() + guides(fill = FALSE)
print(p)
aux <- dev.off()
```
  
###T-tests by trial type and age group
```{r}
d <- data_exp2 %>%
  mutate(correct = as.numeric(as.character(correct)))

d <- aggregate(correct ~ type + agegroup +Subj_ID, data=d, mean)

#tests between quantifiers
#all and some
t.test(subset(d, agegroup=="3.0--3.5" & type=="All")$correct, 
       subset(d, agegroup=="3.0--3.5" & type=="Some")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="3.5--4.0" & type=="All")$correct, 
       subset(d, agegroup=="3.5--4.0"& type=="Some")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.0--4.5" & type=="All")$correct, 
       subset(d, agegroup=="4.0--4.5" & type=="Some")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.5--5.0" & type=="All")$correct, 
       subset(d, agegroup=="4.5--5.0" & type=="Some")$correct, 
       var.equal = TRUE)

#all and none
t.test(subset(d, agegroup=="3.0--3.5" & type=="All")$correct, 
       subset(d, agegroup=="3.0--3.5" & type=="None")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="3.5--4.0" & type=="All")$correct, 
       subset(d, agegroup=="3.5--4.0" & type=="None")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.0--4.5" & type=="All")$correct, 
       subset(d, agegroup=="4.0--4.5" & type=="None")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.5--5.0" & type=="All")$correct, 
       subset(d, agegroup=="4.5--5.0" & type=="None")$correct, 
       var.equal = TRUE)
```

###T-tests between exp 1 and exp. 2
```{r}
d1 <- data_exp1 %>%
  filter(condition == "Scalar")
d2 <- data_exp2

df1 <- aggregate(correct ~ type + agegroup +  Subj_ID, data=d1, mean)%>%
  spread(type, correct)
df2 <- aggregate(correct ~ type + agegroup +  Subj_ID, data=d2, mean)%>%
  spread(type, correct)

#4-4.5s
t.test(subset(df1, agegroup == "4.0--4.5")$All, subset(df2, agegroup == "4.0--4.5")$All, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.0--4.5")$Implicature, subset(df2, agegroup == "4.0--4.5")$Some, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.0--4.5")$None, subset(df2, agegroup == "4.0--4.5")$None, 
       var.equal = TRUE)

#4.5-5
t.test(subset(df1, agegroup == "4.5--5.0")$All, subset(df2, agegroup == "4.5--5.0")$All, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.5--5.0")$Implicature, subset(df2, agegroup == "4.5--5.0")$Some, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.5--5.0")$None, subset(df2, agegroup == "4.5--5.0")$None, 
       var.equal = TRUE)
```

##Diptests and bimodal distribution
```{r}
ms <- data_exp2 %>%
  group_by(type, Subj_ID)%>%
  mutate(agegroup = agegroup[1]) %>%
  summarise(mean = mean(correct),
            agegroup = agegroup[1])

cs <- cast(ms, Subj_ID + agegroup ~ type, value="mean")

dip.test(cs$Some)
dip.test(cs$None)
dip.test(cs$All)
```

##Incorrect selection 
```{r}
exp2_wrong <- data_exp2 %>%
  filter(correct != 1) %>%
  group_by(agegroup, type, selectionType)%>%
  dplyr::summarise(n=n())%>%
  mutate(n.total = sum(n), prop = n/n.total)

wrong <- exp2_wrong[c(1:9, 11:19, 21),] 
    
#now graph
pdf(file="./exp2_wrong.pdf", width=6, height=3.5)
p <- ggplot(data = wrong, 
       aes(x=selectionType, y=n, fill=selectionType, alpha=agegroup)) +
  geom_bar(stat="identity", position = position_dodge())  +
  ylab("Count of children choosing") + 
  xlab("Selection Type") + facet_wrap(~type) + 
  theme_bw(base_size=10) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_alpha_manual(values=c(.5,.625,.725,1)) + guides(fill = FALSE) +
  scale_fill_solarized() + scale_alpha_manual(values=c(0.5,.625, .725, 1), 
                     guide = guide_legend(title = "Age group (years)")) + 
  labs(x = "Trial Type", y = "Mean Correct")
print(p)
aux <- dev.off()
```

##Correlations (full)

```{r}
cor.test(cs$Some, cs$None)

cs %>% group_by(agegroup) %>% 
	summarise(r = cor.test(None, Some)$estimate,
			  p = cor.test(None, Some)$p.value)
```

##Logistic regression
```{r}
data_exp2 %<>%
  mutate(age.c = scale(age, center=TRUE, scale=FALSE))

gl.int <- glmer(correct ~  type * age.c 
			+ (type | Subj_ID), 
			data=data_exp2, family=binomial)
summary(gl.int)

gl.norand <- glmer(correct ~  type * age.c 
			+ (1 | Subj_ID), 
			data=data_exp2, family=binomial)
summary(gl.norand)
```

#Experiment 3 - Scalar Implicature main analyses
##Read in data - Scalar Implicature
```{r}
#reading in the original wide-form dataframe
d3 <- read.csv("../data/SI_coding.csv")

#fill in the selection types for easier analyses
d3 %<>%
  mutate(carrot_selection = factor(carrot_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")), 
         hat_selection = factor(hat_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         cookies_selection = factor(cookies_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         trains_selection = factor(trains_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         cats_selection = factor(cats_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")),
         purses_selection = factor(purses_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         keys_selection = factor(keys_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         shirts_selection = factor(shirts_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")),
         breads_selection = factor(breads_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         horses_selection = factor(horses_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         bears_selection= factor(bears_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         frogs_selection = factor(frogs_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         plates_selection = factor(plates_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         books_selection = factor(books_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         elephants_selection = factor(elephants_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")),
         lamps_selection = factor(lamps_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         bananas_selection = factor(bananas_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")), 
         butterflies_selection = factor(butterflies_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")))

d2=melt.data.frame(d3,c("sub_ID","test_age", "agegroup","ethnicity", "gender"),c("carrot", "hat", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", "carrot_selection", "hat_selection", "cookies_selection", "trains_selection", "cats_selection", "purses_selection",  "keys_selection", "shirts_selection", "breads_selection", "horses_selection", "bears_selection", "frogs_selection", "plates_selection", "books_selection", "elephants_selection", "lamps_selection", "bananas_selection", "butterflies_selection", "carrot_type", "hat_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))


#making a respectable df  
onethird <- (1/3)*nrow(d2)
data <- d2[1:onethird,]
data$selection <- d2$value[(onethird+1):(onethird*2)]
data$type <- d2$value[(2*onethird+1):nrow(d2)]
names(data)[6] <- "item"
names(data)[7] <- "SI_correct"
data$correct <- data$SI_correct==1

#filtering out NAs, adding agesplit
data %<>%
  filter(sub_ID != "", correct != "NA")%>%
  mutate(agegroup = factor(agegroup, levels = c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years"), 
                           labels = c("3.0--3.5", "3.5--4.0", "4.0--4.5", "4.5--5.0")), 
         selection = factor(selection, levels = c("all", "some", "none"), 
                            labels = c("All", "Some", "None")), 
         type = factor(type, levels = c("control_all", "implicature", "control_none"), 
                       labels = c("All", "Some", "None")), 
         SI_correct = as.numeric(SI_correct),
         test = "Scalar Implicature")

data_si <- data
```

###Demographic information
```{r}
#Find the Mean and median ages
exp3_demo <- data_si %>%
  distinct(agegroup, test_age, gender, ethnicity, sub_ID)%>%
  group_by(agegroup)%>%
  summarise(n = n(), 
            n_female = sum(gender == "f"), 
            n_male = sum(gender == "m"), 
            mean_age = mean(test_age), 
            median_age = median(test_age), 
            sd_age = sd(test_age), 
            n_white = sum(ethnicity == "white"), 
            n_asian = sum(ethnicity == "asian"), 
            n_black = sum(ethnicity == " black"), 
            n_other = sum(ethnicity == "mixed" | ethnicity == "other"), 
            n_na = sum(is.na(ethnicity)))


#use this dataframe for stats
data_si <- data %>%
  mutate(test = "Scalar Implicature")
```

##Mean performance by trial type and age
```{r}
ms_exp3 <- data_si %>%
  group_by(type, agegroup)%>%
  multi_boot_standard("correct", na.rm=T)


#plot
pdf(file="./exp3_SIperformance.pdf", width=6, height=3.5)
p <- ggplot(data = ms_exp3, aes(x=type, y=mean, fill=type, alpha=agegroup)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  geom_linerange(aes(ymin = ci_lower,
                      ymax = ci_upper),
                  size = .3,
                  show.legend = FALSE,
                 position=position_dodge(width = 0.9)) +
  theme_bw(base_size = 10) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_alpha_manual(values=c(0.5,.625, .725, 1), 
                     guide = guide_legend(title = "Age group (years)")) + 
  labs(x = "Trial Type", y = "Mean Correct") +
  scale_fill_solarized() + guides(fill = FALSE)
aux <- dev.off()
```

##T-tests
###Testing against Ali's original data
```{r}
#first create a df 
#aggregate correct repsonses 
df1 <- aggregate(correct ~ type + agegroup +  Subj_ID, data=data_exp2, mean)%>%
  spread(type, correct)
df2 <- aggregate(correct ~ type + agegroup +  sub_ID, data=data_si, mean)%>%
  spread(type, correct)

#tests across age groups
#3-3.5
t.test(subset(df1, agegroup == "3.0--3.5")$All, subset(df2, agegroup == "3.0--3.5")$All, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "3.0--3.5")$Some, subset(df2, agegroup == "3.0--3.5")$Some, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "3.0--3.5")$None, subset(df2, agegroup == "3.0--3.5")$None, 
       var.equal = TRUE)

#3.5-4
t.test(subset(df1, agegroup == "3.5--4.0")$All, subset(df2, agegroup == "3.5--4.0")$All, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "3.5--4.0")$Some, subset(df2, agegroup == "3.5--4.0")$Some, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "3.5--4.0")$None, subset(df2, agegroup == "3.5--4.0")$None, 
       var.equal = TRUE)

#4-4.5
t.test(subset(df1, agegroup == "4.0--4.5")$All, subset(df2, agegroup == "4.0--4.5")$All, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.0--4.5")$Some, subset(df2, agegroup == "4.0--4.5")$Some, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.0--4.5")$None, subset(df2, agegroup == "4.0--4.5")$None, 
       var.equal = TRUE)

#4.5-5
t.test(subset(df1, agegroup == "4.5--5.0")$All, subset(df2, agegroup == "4.5--5.0")$All, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.5--5.0")$Some, subset(df2, agegroup == "4.5--5.0")$Some, 
       var.equal = TRUE)
t.test(subset(df1, agegroup == "4.5--5.0")$None, subset(df2, agegroup == "4.5--5.0")$None, 
       var.equal = TRUE)
```

###T-tests across trial types within agegroups with exp 3 data
```{r}
d <- data_si 

d <- aggregate(correct ~ type + agegroup +sub_ID, data=d, mean)

#tests between quantifiers
#all and some
t.test(subset(d, agegroup=="3.0--3.5" & type=="All")$correct, 
       subset(d, agegroup=="3.0--3.5" & type=="Some")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="3.5--4.0" & type=="All")$correct, 
       subset(d, agegroup=="3.5--4.0"& type=="Some")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.0--4.5" & type=="All")$correct, 
       subset(d, agegroup=="4.0--4.5" & type=="Some")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.5--5.0" & type=="All")$correct, 
       subset(d, agegroup=="4.5--5.0" & type=="Some")$correct, 
       var.equal = TRUE)

#all and none
t.test(subset(d, agegroup=="3.0--3.5" & type=="All")$correct, 
       subset(d, agegroup=="3.0--3.5" & type=="None")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="3.5--4.0" & type=="All")$correct, 
       subset(d, agegroup=="3.5--4.0" & type=="None")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.0--4.5" & type=="All")$correct, 
       subset(d, agegroup=="4.0--4.5" & type=="None")$correct, 
       var.equal = TRUE)
t.test(subset(d, agegroup=="4.5--5.0" & type=="All")$correct, 
       subset(d, agegroup=="4.5--5.0" & type=="None")$correct, 
       var.equal = TRUE)
```

##Diptest for bimodal performance
```{r}
ms3 <- data_si %>%
  group_by(type, sub_ID) %>%
  summarise(mean = mean(correct), 
            agegroup = agegroup[1])

cs <- cast(ms3, sub_ID + agegroup ~ type, value="mean")

dip.test(cs$Some)
dip.test(cs$None)
dip.test(cs$All)
```

##Correlations (full)
```{r}
cor.test(cs$Some, cs$None)

cs %>% group_by(agegroup) %>% 
	summarise(r = cor.test(None, Some)$estimate,
			  p = cor.test(None, Some)$p.value)
```
##Incorrect selections 
```{r}
si_wrong <- data_si %>%
  filter(correct != "TRUE") %>%
  group_by(agegroup, type, selection)%>%
  dplyr::summarise(n=n())%>%
  mutate(n.total = sum(n), prop = n/n.total)

pdf(file="./exp3_SIwrong.pdf", width=6, height=3.5)
p <- ggplot(data = si_wrong, 
       aes(x=selection, y=n, fill=selection, alpha=agegroup)) +
  geom_bar(stat="identity", position = position_dodge())  +
  ylab("Count of children choosing") + 
  xlab("Selection Type") + facet_wrap(~type) + 
  theme_bw(base_size=10) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  scale_alpha_manual(values=c(.5,.625,.725,1)) + guides(fill = FALSE) +
  scale_fill_solarized() + scale_alpha_manual(values=c(0.5,.625, .725, 1), 
                     guide = guide_legend(title = "Age group (years)")) + 
  labs(x = "Trial Type", y = "Count of children choosing")
print(p)
aux <- dev.off()
```  

#Experiment 3 - Give-Quantifier full analyses
```{r}
#read in and establish dataframe
d1 <- read.csv("../data/GQ_coding.csv")
d1[,c(8,10,12,14,16,18,20,22, 31, 32, 33, 34)] <- sapply(d1[,c(8,10,12,14,16,18,20,22, 31, 32, 33, 34)],as.character) #for unknown reasons this is necessary for melt.data.frame now

#change to long form
d2=melt.data.frame(d1,c("sub_ID", "test_age","agegroup", "condition", "training"),c("X1_condition", "X2_condition", "X3_condition", "X4_condition", "X5_condition", "X6_condition",  "X7_condition", "X8_condition", "X1_given", "X2_given", "X3_given", "X4_given", "X5_given", "X6_given",  "X7_given", "X8_given", "X1_correct", "X2_correct", "X3_correct", "X4_correct", "X5_correct", "X6_correct",  "X7_correct", "X8_correct"))

#making a respectable df  
onethird <- (1/3)*nrow(d2)
data <- d2[1:onethird,]
data$selection <- d2$value[(onethird+1):(onethird*2)]
data$type <- d2$value[(2*onethird+1):nrow(d2)]
names(data)[6] <- "trial"
names(data)[7] <- "prompt"
names(data)[8] <- "num_given"
names(data)[9] <- "GQ_correct"

#filtering data, creating age breaks
data %<>%
  filter(sub_ID != "", num_given != "N/A")%>%
  mutate(num_given = as.numeric(as.character(num_given)), 
         GQ_correct = as.numeric(as.character(GQ_correct)), 
         test = "Give-Quantifier", 
         agegroup = factor(agegroup, levels = c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years"), 
                           labels = c("3.0--3.5", "3.5--4.0", "4.0--4.5", "4.5--5.0")), 
         prompt = factor(prompt, levels = c("all", "some", "none", "most"), 
                            labels = c("All", "Some", "None", "Most")))

data_gq <- data
```

##Mean correct by age and trial type 
"Correct" responses outlined in Barner, Chow, & Yang (2009).
```{r}
ms_gq <- data_gq %>%
  filter(prompt != "Most") %>%
  group_by(prompt, agegroup)%>%
  multi_boot_standard("GQ_correct", na.rm=T)

pdf(file="./exp3_GQperf.pdf", width=6, height=3.5)
p <- quartz()
ggplot(data = ms_gq, 
       aes(x=prompt, y=mean, fill=prompt, alpha = `agegroup`)) +
  geom_bar(stat="identity", position = position_dodge()) +
  geom_linerange(aes(ymin = ci_lower,
                      ymax = ci_upper),
                  size = .3,
                  show.legend = FALSE,
                 position=position_dodge(width = 0.9)) +
  ylab("Proportion correct") + 
  xlab("Quantifier Prompt") +
  theme_bw(base_size=18) + 
  theme(axis.title.x = element_text(size=16),
        axis.title.y  = element_text(size=16),
        legend.title=element_text(size=14), 
        legend.text=element_text(size=14), 
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank()) +
  scale_alpha_manual(values=c(.5,.625,.725,1)) + guides(fill = FALSE) +
  scale_fill_solarized()
print(p)
aux <- dev.off()
```