title: "SI_stats"
output: html_document
---
Horowitz, Mekler, Schneider, Frank, etc. 
Analyses for Scalar Implicature, Give-Quantifier, and DCCS


Set up Rmd parameters
```{r}
library(knitr)
opts_chunk$set(cache=TRUE, message=FALSE, warning=FALSE, error=TRUE)
```

Preliminaries
```{r}
rm(list=ls())
library(ggplot2)
library(reshape)
library(plyr)
library(dplyr)
library(stringr)
library(tidyr)
library(markdown)
library(directlabels)
library(magrittr)
library(bootstrap)
library(RCurl)
library(langcog)
library(diptest)


theme_set(theme_bw())
```

Experiment 1 - read in data
```{r}
d <- read.csv("../data/implicatures_adhocScalar_data.csv")

#fill in the selection types for easier analyses
d_exp1=melt.data.frame(d,c("Subj_ID", "age","agegroup", "list"),c("carrots", "hats", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", 
"carrots_condition", "hats_condition", "cookies_condition", "trains_condition", "cats_condition", "purses_condition",  "keys_condition", "shirts_condition", "breads_condition", "horses_condition", "bears_condition", "frogs_condition", "plates_condition", "books_condition", "elephants_condition", "lamps_condition", "bananas_condition", "butterflies_condition", 
"carrots_type", "hats_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))

data_exp1 <- d_exp1[1:864,] 
data_exp1$condition <- d_exp1$value[865:1728]
data_exp1$type <- d_exp1$value[1729:2592]
names(data_exp1)[5] <- "item"
names(data_exp1)[6] <- "correct"

attach(data_exp1)
data_exp1$trial_type[type == "implicature"] <- "implicature"
data_exp1$trial_type[type != "implicature"] <- "control"
detach(data_exp1)

#rename agegroups for prettier graphs
data_exp1$agegroup %<>%
  str_replace("4.0--4.5", "4-4.5 years")%>%
  str_replace("4.5--5.0", "4.5-5 years")

data_exp1 %<>%
  rename(Age = agegroup)

#age groups
# data_exp1 %<>%
#   filter(Subj_ID != "", correct != "NA") %>%
#   mutate(agesplit = cut(age, breaks=c(4, 4.5, 5)),
#          agesplit = factor(agesplit,
#                            labels=c("4-4.5 years", "4.5-5 years"))) %>%
#   filter(agesplit != "NA")

#renaming for graphs
data_exp1$type <- factor(data_exp1$type, 
					levels = c("implicature","control_comparison", 
					"control_distractor",
					"control_none","control_unambiguous", "control_all"), 
					labels = c("Implicature","Comparison", 
					"Distractor",
					"None","Unambig. Some", "All"))

data_exp1$condition <- factor(data_exp1$condition, 
					levels = c("adhoc","scalar"), 
					labels = c("Ad-hoc","Scalar"))

# data_exp1 %<>%
#   dplyr::rename(Age = agesplit)
```

EXP 1 - T-tests
```{r}
#look at only SI trials
d <- data_exp1 %>%
  filter(condition == "Scalar")%>%
  mutate(correct = as.numeric(correct))

d <- aggregate(correct ~ type + Age +  Subj_ID, data=d, mean)

# ##First test against chance - no longer included, as the definition of "Chance" in this study is difficulty
# #All
# t.test(subset(d, Age=="4-4.5 years" & type=="All")$correct, mu=0.5)
# t.test(subset(d, Age=="4.5-5 years" & type=="All")$correct, mu=0.5)
# 
# #Some
# t.test(subset(d, Age=="4-4.5 years" & type=="Implicature")$correct, mu=0.5)
# t.test(subset(d, Age=="4.5-5 years"  & type=="Implicature")$correct, mu=0.5)
# 
# #none
# t.test(subset(d, Age=="4-4.5 years" & type=="None")$correct, mu=0.5)
# t.test(subset(d, Age=="4.5-5 years" & type=="None")$correct, mu=0.5)

#t-tests against "all"
#4-4.5
#all-some
t.test(subset(d, Age == "4-4.5 years" & type == "All")$correct,
       subset(d, Age == "4-4.5 years" & type == "Implicature")$correct,
       var.equal = TRUE)
#all-none
t.test(subset(d, Age == "4-4.5 years" & type == "All")$correct,
       subset(d, Age == "4-4.5 years" & type == "None")$correct,
       var.equal = TRUE)
#all-unambig.some
t.test(subset(d, Age == "4-4.5 years" & type == "All")$correct,
       subset(d, Age == "4-4.5 years" & type == "Unambig. Some")$correct,
       var.equal = TRUE)

#4.5-5
#all-some
t.test(subset(d, Age == "4.5-5 years" & type == "All")$correct,
       subset(d, Age == "4.5-5 years" & type == "Implicature")$correct,
       var.equal = TRUE)
#all-none
t.test(subset(d, Age == "4.5-5 years" & type == "All")$correct,
       subset(d, Age == "4.5-5 years" & type == "None")$correct,
       var.equal = TRUE)
#all-unambig.some
t.test(subset(d, Age == "4.5-5 years" & type == "All")$correct,
       subset(d, Age == "4.5-5 years" & type == "Unambig. Some")$correct,
       var.equal = TRUE)
```

T-tests: Scalar vs. ad-hoc
```{r}
d <- data_exp1 %>%
  mutate(correct = as.numeric(correct))

d <- aggregate(correct ~ type + Age + condition + Subj_ID, data=d, mean)

#comparison - ad-hoc implicature vs. scalar
#4-4.5
t.test(subset(d, Age == "4-4.5 years" & type == "Implicature" 
              & condition == "Ad-hoc")$correct,
       subset(d, Age == "4-4.5 years" & type == "Implicature" 
              & condition == "Scalar")$correct,
       var.equal = TRUE)

#4.5-5
t.test(subset(d, Age == "4.5-5 years" & type == "Implicature" 
              & condition == "Ad-hoc")$correct,
       subset(d, Age == "4.5-5 years" & type == "Implicature" 
              & condition == "Scalar")$correct,
       var.equal = TRUE)
```

EXP 1 - Diptest
```{r}
data_exp1 %<>%
  mutate(correct = as.numeric(correct))

ms <- ddply(data_exp1, .(type, condition, Subj_ID), summarise, 
	mean = mean(correct),
	Age = Age[1])

ms %<>%
  filter(condition == "Scalar")

names(ms) <- c("type", "condition", "Subj_ID", "mean", "Age")

cs <- cast(ms, Subj_ID + Age ~ type + condition, value="mean") %>%
  rename(control_none_scalar = None_Scalar, implicature_scalar = Implicature_Scalar, control_all_scalar = All_Scalar)

dip.test(cs$implicature_scalar)
dip.test(cs$control_none_scalar)
dip.test(cs$control_all_scalar)
```

EXP 1 - correlations (full)
```{r}
#full correlations
cor.test(cs$control_none_scalar, cs$implicature_scalar)
cor.test(cs$control_all_scalar, cs$implicature_scalar)
cor.test(cs$control_none_scalar, cs$control_all_scalar)

#by age
#none-some
cs %>% group_by(Age) %>% 
	summarise(r = cor.test(control_none_scalar, implicature_scalar)$estimate,
			  p = cor.test(control_none_scalar, implicature_scalar)$p.value)
#all-some
cor.test(cs$control_all_scalar, cs$implicature_scalar)
cs %>% group_by(Age) %>% 
	summarise(r = cor.test(control_all_scalar, implicature_scalar)$estimate,
			  p = cor.test(control_all_scalar, implicature_scalar)$p.value)
#all-none
cor.test(cs$control_all_scalar, cs$control_none_scalar)
cs %>% group_by(Age) %>% 
	summarise(r = cor.test(control_all_scalar, control_none_scalar)$estimate,
			  p = cor.test(control_all_scalar, control_none_scalar)$p.value)		
```

Exp1 - model
```{r}
#center age to facilitate model fit
data_exp1 %<>%
  mutate(age.c = scale(age, center = TRUE, scale=FALSE))

library(lme4)
gl <- glmer(correct ~ trial_type * condition * age.c  + 
              (trial_type | Subj_ID), data=data_exp1, 
            family=binomial, control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))) 
#change optimizer, otherwise model won't converge
summary(gl)
```

Experiment 2
Read in data
```{r}
d2 <- read.csv("../data/implicatures_scalarOnly_data.csv")

data_exp2=melt.data.frame(d2,c("Subj_ID","age","agegroup","list"),c("carrots", "hats", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", 
"carrots_selectionType", "hats_selectionType", "cookies_selectionType", "trains_selectionType", "cats_selectionType", "purses_selectionType",  "keys_selectionType", "shirts_selectionType", "breads_selectionType", "horses_selectionType", "bears_selectionType", "frogs_selectionType", "plates_selectionType", "books_selectionType", "elephants_selectionType", "lamps_selectionType", "bananas_selectionType", "butterflies_selectionType", 
"carrots_type", "hats_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))

data <- data_exp2[1:918,] 
data$selectionType <- data_exp2$value[919:1836]
data$type <- data_exp2$value[1837:2754]
names(data)[5] <- "item"
names(data)[6] <- "correct"

data_exp2 <- data

attach(data_exp2)
data_exp2$trial_type[type == "some"] <- "implicature"
data_exp2$trial_type[type != "some"] <- "control"
detach(data_exp2)

#rename agegroups
data_exp2$agegroup %<>%
  str_replace("3.0--3.5", "3-3.5 years")%>%
  str_replace("3.5--4.0", "3.5-4 years")%>%
  str_replace("4.0--4.5", "4-4.5 years")%>%
  str_replace("4.5--5.0", "4.5-5 years")

data_exp2 %<>%
  rename(Age = agegroup)

# data_exp2 %<>%
#   filter(Subj_ID != "", correct != "NA") %>%
#   mutate(agesplit = cut(age, breaks=c(3, 3.5, 4, 4.5, 5)),
#          agesplit = factor(agesplit,
#                            labels=c("3-3.5 years", "3.5-4 years", "4-4.5 years", "4.5-5 years"))) %>%
#   filter(agesplit != "NA")

#renaming for graphs
data_exp2$type <- factor(data_exp2$type, 
					levels = c("all","none", 
					"some"), 
					labels = c("All","None", 
					"Some"))
data_exp2$selectionType <- factor(data_exp2$selectionType, 
					levels = c("all","none", 
					"some"), 
					labels = c("All","None", 
					"Some"))
# data_exp2$trial_type <- factor(data_exp2$trial_tyçpe, 
#                                levels = c ("control", "implicature"), 
#                                labels = c("Control", "Implicature")) 

# data_exp2 %<>%
#   rename(Age = agesplit)
```

tests against chance
```{r}

##First test against chance
d <- data_exp2 %>%
  mutate(correct = as.numeric(as.character(correct)))

d <- aggregate(correct ~ type + Age +  Subj_ID, data=d, mean)
# #All
# t.test(subset(d, Age=="3-3.5 years" & type=="All")$correct, mu=0.5)
# t.test(subset(d, Age=="3.5-4 years" & type=="All")$correct, mu=0.5)
# t.test(subset(d, Age=="4-4.5 years" & type=="All")$correct, mu=0.5)
# t.test(subset(d, Age=="4.5-5 years" & type=="All")$correct, mu=0.5)
# 
# #Some
# t.test(subset(d, Age=="3-3.5 years"  & type=="Some")$correct, mu=0.5)
# t.test(subset(d, Age=="3.5-4 years" & type=="Some")$correct, mu=0.5)
# t.test(subset(d, Age=="4-4.5 years" & type=="Some")$correct, mu=0.5)
# t.test(subset(d, Age=="4.5-5 years" & type=="Some")$correct, mu=0.5)
# 
# #none
# t.test(subset(d, Age=="3-3.5 years"  & type=="None")$correct, mu=0.5)
# t.test(subset(d, Age=="3.5-4 years" & type=="None")$correct, mu=0.5)
# t.test(subset(d, Age=="4-4.5 years" & type=="None")$correct, mu=0.5)
# t.test(subset(d,Age=="4.5-5 years" & type=="None")$correct, mu=0.5)

#tests between quantifiers
#all and some
t.test(subset(d, Age=="3-3.5 years" & type=="All")$correct, 
       subset(d, Age=="3-3.5 years" & type=="Some")$correct)
t.test(subset(d, Age=="3.5-4 years" & type=="All")$correct, 
       subset(d, Age=="3.5-4 years" & type=="Some")$correct)
t.test(subset(d, Age=="4-4.5 years" & type=="All")$correct, 
       subset(d, Age=="4-4.5 years" & type=="Some")$correct)
t.test(subset(d, Age=="4.5-5 years" & type=="All")$correct, 
       subset(d, Age=="4.5-5 years" & type=="Some")$correct)

#all and none
t.test(subset(d, Age=="3-3.5 years" & type=="All")$correct, 
       subset(d, Age=="3-3.5 years" & type=="None")$correct)
t.test(subset(d, Age=="3.5-4 years" & type=="All")$correct, 
       subset(d, Age=="3.5-4 years" & type=="None")$correct)
t.test(subset(d, Age=="4-4.5 years" & type=="All")$correct, 
       subset(d, Age=="4-4.5 years" & type=="None")$correct)
t.test(subset(d, Age=="4.5-5 years" & type=="All")$correct, 
       subset(d, Age=="4.5-5 years" & type=="None")$correct)
```

Create a dataframe to compare performance between Exp 1 scalar trials and experiment 2
```{r}
d1 <- data_exp1 
d2 <- data_exp2%>%
  mutate(correct=as.numeric(correct))

df1 <- aggregate(correct ~ type + Age +  Subj_ID, data=d1, mean)%>%
  spread(type, correct)
df2 <- aggregate(correct ~ type + Age +  Subj_ID, data=d2, mean)%>%
  spread(type, correct)

```

Compare performance on scalar trials between Exp1 and Exp2
```{r}

#Split this df into agegroups
old1 <- df1 %>%
  filter(Age == "4-4.5 years")

old2 <- df2 %>%
  filter(Age == "4-4.5 years")

#4-4.5s
t.test(old1$All, old2$All)
t.test(old1$Implicature, old2$Some)
t.test(old1$None, old2$None)

#4.5-5s
old3 <- df1 %>%
  filter(Age == "4.5-5 years")

old4 <- df2 %>%
  filter(Age == "4.5-5 years")

t.test(old3$All, old4$All)
t.test(old3$Implicature, old4$Some)
t.test(old3$None, old4$None)

```

Exp 2 models
```{r}
data_exp2 %<>%
  mutate(correct = as.integer(correct),
         age.c = scale(age, center=TRUE, scale=FALSE))
gl.int <- glmer(correct ~  type * age.c 
			+ (type | Subj_ID), 
			data=data_exp2, family=binomial)
summary(gl.int)

gl.norand <- glmer(correct ~  type * age.c 
			+ (1 | Subj_ID), 
			data=data_exp2, family=binomial)
summary(gl.norand)

```

Diptests
```{r}
data_exp2 %<>%
  mutate(correct = as.numeric(correct))

ms <- ddply(data_exp2, .(type, Subj_ID), summarise, 
	mean = mean(correct),
	Age = Age[1])

names(ms) <- c("type", "Subj_ID", "mean", "Age")

cs <- cast(ms, Subj_ID + Age ~ type, value="mean")

dip.test(cs$Some)
dip.test(cs$None)
dip.test(cs$All)
```

Correlations
```{r}
cor.test(cs$Some, cs$None)

cs %>% group_by(Age) %>% 
	summarise(r = cor.test(None, Some)$estimate,
			  p = cor.test(None, Some)$p.value)

```
Experiment 3 
Set up data
Scalar Implicature
```{r}
#reading in the original wide-form dataframe
d1 <- read.csv("../data/SI_coding.csv")

#fill in the selection types for easier analyses
d1 %<>%
  mutate(carrot_selection = factor(carrot_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")), 
         hat_selection = factor(hat_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         cookies_selection = factor(cookies_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         trains_selection = factor(trains_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         cats_selection = factor(cats_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")),
         purses_selection = factor(purses_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         keys_selection = factor(keys_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         shirts_selection = factor(shirts_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")),
         breads_selection = factor(breads_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         horses_selection = factor(horses_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         bears_selection= factor(bears_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")),
         frogs_selection = factor(frogs_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         plates_selection = factor(plates_selection, levels=c(1, 2, 3), labels = c("all", "some", "none")), 
         books_selection = factor(books_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         elephants_selection = factor(elephants_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")),
         lamps_selection = factor(lamps_selection, levels=c(1, 2, 3), labels = c("none", "all", "some")), 
         bananas_selection = factor(bananas_selection, levels=c(1, 2, 3), labels = c("some", "all", "none")), 
         butterflies_selection = factor(butterflies_selection, levels=c(1, 2, 3), labels = c("none", "some", "all")))

d2=melt.data.frame(d1,c("sub_ID","test_age", "agegroup","training"),c("carrot", "hat", "cookies", "trains", "cats", "purses",  "keys", "shirts", "breads", "horses", "bears", "frogs", "plates", "books", "elephants", "lamps", "bananas", "butterflies", "carrot_selection", "hat_selection", "cookies_selection", "trains_selection", "cats_selection", "purses_selection",  "keys_selection", "shirts_selection", "breads_selection", "horses_selection", "bears_selection", "frogs_selection", "plates_selection", "books_selection", "elephants_selection", "lamps_selection", "bananas_selection", "butterflies_selection", "carrot_type", "hat_type", "cookies_type", "trains_type", "cats_type", "purses_type",  "keys_type", "shirts_type", "breads_type", "horses_type", "bears_type", "frogs_type", "plates_type", "books_type", "elephants_type", "lamps_type", "bananas_type", "butterflies_type"))


#making a respectable df  
onethird <- (1/3)*nrow(d2)
data <- d2[1:onethird,]
data$selection <- d2$value[(onethird+1):(onethird*2)]
data$type <- d2$value[(2*onethird+1):nrow(d2)]
names(data)[5] <- "item"
names(data)[6] <- "SI_correct"
data$correct <- data$SI_correct==1

#filtering out NAs, adding agesplit
data %<>%
  filter(sub_ID != "", correct != "NA") 

data %<>%
  rename(Age = agegroup)

#renaming for better-looking graphs
data$type %<>%
  str_replace("control_all", "All")%>%
  str_replace("control_none", "None")%>%
  str_replace("implicature", "Implicature")

data$selection %<>%
  str_replace("all", "All")%>%
  str_replace("none", "None")%>%
  str_replace("some", "Some")

#Find the Mean and median ages
age <- data %>%
  dplyr::select(sub_ID, test_age, Age) %>%
  dplyr::distinct() %>%
  group_by(Age)%>%
  summarise(n=n(), avg = mean(test_age))

#use this dataframe for stats
data_si <- data %>%
  mutate(test = "Scalar Implicature")

#age stats
age <- data_si %>%
  group_by(Age)%>%
  summarise(mean = mean(test_age), median = median(test_age), sd = sd(test_age))
```

GQ
```{r}
#read in and establish dataframe
d1 <- read.csv("../data/GQ_coding.csv")
d1[,c(8,10,12,14,16,18,20,22, 31, 32, 33, 34)] <- sapply(d1[,c(8,10,12,14,16,18,20,22, 31, 32, 33, 34)],as.character) #for unknown reasons this is necessary for melt.data.frame now

#change to long form
d2=melt.data.frame(d1,c("sub_ID", "test_age","agegroup", "condition", "training"),c("X1_condition", "X2_condition", "X3_condition", "X4_condition", "X5_condition", "X6_condition",  "X7_condition", "X8_condition", "X1_given", "X2_given", "X3_given", "X4_given", "X5_given", "X6_given",  "X7_given", "X8_given", "X1_correct", "X2_correct", "X3_correct", "X4_correct", "X5_correct", "X6_correct",  "X7_correct", "X8_correct"))

#making a respectable df  
onethird <- (1/3)*nrow(d2)
data <- d2[1:onethird,]
data$selection <- d2$value[(onethird+1):(onethird*2)]
data$type <- d2$value[(2*onethird+1):nrow(d2)]
names(data)[6] <- "trial"
names(data)[7] <- "prompt"
names(data)[8] <- "num_given"
names(data)[9] <- "GQ_correct"

#filtering data, creating age breaks
data %<>%
  filter(sub_ID != "", num_given != "N/A")%>%
  rename(Age = agegroup)

#this is because num_given is a factor - need to change to a number - need to do this for standard error
data$num_given <- as.character(data$num_given)
data$num_given <- as.numeric(data$num_given)
data$GQ_correct <-as.character(data$GQ_correct)
data$GQ_correct <- as.numeric(data$GQ_correct)

#renaming things for prettier graphs
data$prompt %<>%
  str_replace("all", "All")%>%
  str_replace("most", "Most")%>%
  str_replace("some", "Some")%>%
  str_replace("none", "None")

#creating dataframe for analyses
data_gq <- data %>%
  mutate(test = "Give-Quantifier")
```
DCCS
```{r}
#wide-form
d1 <- read.csv("../data/DCCS_coding.csv")
#long form
d2=melt.data.frame(d1,c("sub_ID","test_age", "agegroup", "condition"),c("pre_1", "pre_2", "pre_3", "pre_4", "pre_5", "pre_6",  "post_1", "post_2", "post_3", "post_4", "post_5", "post_6"))

#filtering data, creating age breaks
data <- d2 %>%
  filter(sub_ID != "") 

data %<>%
  rename(Age = agegroup)

#renaming things
names(data)[5] <- "trial_type"
names(data)[6] <- "DCCS_correct"

#df for further analyses
data_dccs <- data
data_dccs$test <- "DCCS"
  
#rename trials
tmp1 <- unlist(data$trial_type)%>%
  str_replace("pre_1", "pre")%>%
  str_replace("pre_2", "pre")%>%
  str_replace("pre_3", "pre")%>%
  str_replace("pre_4", "pre")%>%
  str_replace("pre_5", "pre")%>%
  str_replace("pre_6", "pre")%>%
  str_replace("post_1", "post")%>%
  str_replace("post_2", "post")%>%
  str_replace("post_3", "post")%>%
  str_replace("post_4", "post")%>%
  str_replace("post_5", "post")%>%
  str_replace("post_6", "post")

tmp <- as.data.frame(tmp1) %>%
  dplyr::rename(switch_type = tmp1)
tmp2 <- bind_cols(data, tmp)
data <- tmp2

#renaming for prettier graphs
data$switch_type %<>%
  str_replace("post", "Post-switch")%>%
  str_replace("pre", "Pre-switch")

data$switch_type <- as.factor(data$switch_type)
data_dccs <- data
```

Test SI against Ali's data
```{r}
#first create a df 
d1 <- data_exp2 %>%
  mutate(correct=as.numeric(correct))
d2 <- data_si%>%
  mutate(correct=as.numeric(correct))
#aggregate correct repsonses 
df1 <- aggregate(correct ~ type + Age+  Subj_ID, data=d1, mean)%>%
  spread(type, correct)
df2 <- aggregate(correct ~ type + Age +  sub_ID, data=d2, mean)%>%
  spread(type, correct)

#split into age groups - this is pretty clunky, but it works
old1 <- df1 %>%
  filter(Age == "3-3.5 years")

old2 <- df2 %>%
  filter(Age == "3-3.5 years")

old3 <- df1 %>%
  filter(Age == "3.5-4 years")

old4 <- df2 %>%
  filter(Age == "3.5-4 years")

old5 <- df1 %>%
  filter(Age == "4-4.5 years")

old6 <- df2 %>%
  filter(Age == "4-4.5 years")

old7 <- df1 %>%
  filter(Age == "4.5-5 years")

old8 <- df2 %>%
  filter(Age == "4.5-5 years")

#tests across age groups
#3-3.5s
t.test(old1$All, old2$All, var.equal = TRUE)
t.test(old1$Some, old2$Implicature, var.equal = TRUE)
t.test(old1$None, old2$None, var.equal = TRUE)

#3.5-4s
t.test(old3$All, old4$All, var.equal = TRUE)
t.test(old3$Some, old4$Implicature, var.equal = TRUE)
t.test(old3$None, old4$None, var.equal = TRUE)

#4-4.5s
t.test(old5$All, old6$All, var.equal = TRUE)
t.test(old5$Some, old6$Implicature, var.equal = TRUE)
t.test(old5$None, old6$None, var.equal = TRUE)

#4.5-5s
t.test(old7$All, old8$All, var.equal = TRUE)
t.test(old7$Some, old8$Implicature, var.equal = TRUE)
t.test(old7$None, old8$None, var.equal = TRUE)
```

Now our entire Exp 3 dataset
Create wide-form df to do analyses
```{r}
#si df
data_si$SI_correct <- as.character(data_si$SI_correct)
data_si$SI_correct <- as.numeric(data_si$SI_correct)

#scalar implicature task
mss.acc <- data_si %>%
  group_by(sub_ID, type)%>%
  dplyr::summarise(mean = mean(SI_correct), 
                   test_age = test_age[1],
                   Age = Age[1])%>%
  spread(type, mean)

#dccs
mss.acc2 <- data_dccs %>%
  group_by(sub_ID, switch_type)%>%
  dplyr::summarise(mean=mean(DCCS_correct))%>%
  spread(switch_type, mean)

#now gq
#first mean number
mss.acc3 <- data_gq %>%
  group_by(sub_ID, prompt)%>%
  dplyr::summarise(mean_num = mean(num_given)) %>%
  spread(prompt, mean_num)

#then correct
mss.acc4 <- data_gq %>%
  group_by(sub_ID, prompt)%>%
  dplyr::summarise(mean_correct = mean(GQ_correct))%>%
  spread(prompt, mean_correct)

#overall correct for GQ
mss.acc5 <- data_gq %>%
  group_by(sub_ID)%>%
  dplyr::summarise(mean_correct = mean(GQ_correct))%>%
  dplyr::rename(GQ_overall = mean_correct)

#overall correct for SI
mss.acc6 <- data_si %>%
  group_by(sub_ID)%>%
  dplyr::summarise(SI_overall = mean(SI_correct))
  

#bind together
tmp <- right_join(mss.acc, mss.acc2, by = "sub_ID")
tmp1 <- right_join(tmp, mss.acc3, by = "sub_ID") 
tmp2 <- right_join(tmp1, mss.acc5, by = "sub_ID")
tmp3 <- right_join(tmp2, mss.acc6, by="sub_ID")
d_all <- right_join(tmp3, mss.acc4, by = "sub_ID") %>%
  dplyr::rename(SI_none = None.x, 
         SI_all = All.x, 
         SI_implicature = Implicature, 
         GQ_all = All.y, 
         GQ_most = Most.x, 
         GQ_some = Some.x, 
         GQ_none = None.y, 
         GQ_all_correct = All, 
         GQ_most_correct = Most.y, 
         GQ_some_correct = Some.y, 
         GQ_none_correct = None,
         test_age = test_age)

#center age for model fit
d_all %<>%
  mutate(age.c = scale(test_age, scale = FALSE, center = TRUE))
```

Correlations - full
```{r}
#Significant correlation between age and DCCS
cor.test(~d_all$test_age + d_all$`Post-switch`)
#full correlation between some and none
cor.test(~d_all$SI_implicature + d_all$SI_none)
```

Partial correlations for age - SI/GQ and DCCS
```{r}
library(ppcor)
#partial correlation - implicature and dccs
pcor.test(d_all$SI_implicature, d_all$SI_none, d_all$test_age)

pcor.test(d_all$SI_implicature, d_all$`Post-switch`, d_all$test_age)

pcor.test(d_all$SI_none, d_all$`Post-switch`, d_all$test_age)

pcor.test(d_all$SI_all, d_all$`Post-switch`, d_all$test_age)

pcor.test(d_all$GQ_none_correct, d_all$`Post-switch`, d_all$test_age)

pcor.test(d_all$GQ_some_correct, d_all$`Post-switch`, d_all$test_age)

pcor.test(d_all$GQ_most_correct, d_all$`Post-switch`, d_all$test_age)

pcor.test(d_all$GQ_all_correct, d_all$`Post-switch`, d_all$test_age)
```

SI and GQ partial correlations
```{r}
library(ppcor)
pcor.test(d_all$SI_implicature, d_all$GQ_some_correct, d_all$test_age)

pcor.test(d_all$SI_implicature, d_all$GQ_none_correct, d_all$test_age)

pcor.test(d_all$SI_none, d_all$SI_implicature, d_all$test_age)

pcor.test(d_all$SI_none, d_all$GQ_none_correct, d_all$test_age)

pcor.test(d_all$SI_none, d_all$GQ_some_correct, d_all$test_age)
```

T-tests
```{r}
#aggregate mean
df <- data_si %>%
  mutate(correct = as.numeric(as.character(SI_correct)))

d <- aggregate(correct ~ type + Age +  sub_ID, data=df, mean)

d.dccs <- data_dccs %>%
  mutate(correct=as.numeric(as.character(DCCS_correct)))

df.dccs <- aggregate(correct ~ switch_type + Age +  sub_ID, data=d.dccs, mean) 

#tests against All
#all and some
t.test(subset(d, Age=="3-3.5 years" & type=="All")$correct, 
       subset(d, Age=="3-3.5 years" & type=="Implicature")$correct,
       var.equal = TRUE)
t.test(subset(d, Age=="3.5-4 years" & type=="All")$correct, 
       subset(d, Age=="3.5-4 years" & type=="Implicature")$correct,
       var.equal = TRUE)
t.test(subset(d, Age=="4-4.5 years" & type=="All")$correct, 
       subset(d, Age=="4-4.5 years" & type=="Implicature")$correct,
       var.equal = TRUE)
t.test(subset(d, Age=="4.5-5 years" & type=="All")$correct, 
       subset(d, Age=="4.5-5 years" & type=="Implicature")$correct,
       var.equal = TRUE)

#all and none
t.test(subset(d, Age=="3-3.5 years" & type=="All")$correct, 
       subset(d, Age=="3-3.5 years" & type=="None")$correct,
       var.equal = TRUE)
t.test(subset(d, Age=="3.5-4 years" & type=="All")$correct, 
       subset(d, Age=="3.5-4 years" & type=="None")$correct,
       var.equal = TRUE)
t.test(subset(d, Age=="4-4.5 years" & type=="All")$correct, 
       subset(d, Age=="4-4.5 years" & type=="None")$correct,
       var.equal = TRUE)
t.test(subset(d, Age=="4.5-5 years" & type=="All")$correct, 
       subset(d, Age=="4.5-5 years" & type=="None")$correct,
       var.equal = TRUE)

#3-3.5 - SI
t.test(subset(df, Age=="3-3.5 years" & type=="All")$correct, mu=0.5)
t.test(subset(df, Age=="3-3.5 years" & type=="Implicature")$correct, mu=0.5)
t.test(subset(df, Age=="3-3.5 years" & type=="None")$correct, mu=0.5)

#Dccs
t.test(subset(df.dccs, Age=="3-3.5 years" & switch_type=="Post-switch")$correct, mu=0.5)

#3.5-4
t.test(subset(df, Age=="3.5-4 years" & type=="All")$correct, mu=0.5)
t.test(subset(df, Age=="3.5-4 years" & type=="Implicature")$correct, mu=0.5)
t.test(subset(df, Age=="3.5-4 years" & type=="None")$correct, mu=0.5)

#dccs
t.test(subset(df.dccs, Age=="3.5-4 years" & switch_type=="Post-switch")$correct, mu=0.5)

#4-4.5
t.test(subset(df, Age=="4-4.5 years" & type=="All")$correct, mu=0.5)
t.test(subset(df, Age=="4-4.5 years" & type=="Implicature")$correct, mu=0.5)
t.test(subset(df, Age=="4-4.5 years" & type=="None")$correct, mu=0.5)

#dccs
t.test(subset(df.dccs, Age=="4-4.5 years" & switch_type=="Post-switch")$correct, mu=0.5)

#4.5-5
t.test(subset(df, Age=="4.5-5 years" & type=="All")$correct, mu=0.5)
t.test(subset(df, Age=="4.5-5 years" & type=="Implicature")$correct, mu=0.5)
t.test(subset(df, Age=="4.5-5 years" & type=="None")$correct, mu=0.5)

#dccs
t.test(subset(df.dccs, Age=="4.5-5 years" & switch_type=="Post-switch")$correct, mu=0.5)
```


Diptests
```{r}
#scalar implicature
dip.test(d_all$SI_implicature)
dip.test(d_all$SI_all)
dip.test(d_all$SI_none)

#GQ
dip.test(d_all$GQ_some_correct)
dip.test(d_all$GQ_none_correct)
dip.test(d_all$GQ_all_correct)

#break GQ down by age, see if a specific age group is driving this effect
young1 <- d_all%>%
  filter(Age == "3-3.5 years")

dip.test(young1$GQ_some_correct)
dip.test(young1$GQ_none_correct)

young2 <- d_all%>%
  filter(Age == "3.5-4 years")

dip.test(young2$GQ_some_correct)
dip.test(young2$GQ_none_correct)

old1 <- d_all %>%
  filter(Age == "4-4.5 years")

dip.test(old1$GQ_some_correct)
dip.test(old1$GQ_none_correct)

old2 <- d_all %>%
  filter(Age == "4.5-5 years")
dip.test(old2$GQ_some_correct)
dip.test(old2$GQ_none_correct)
```

Logistic regressions
```{r}
# d_all %<>%
#   mutate(`Post-switch` = as.numeric(`Post-switch`))
# summary(glm(SI_overall ~ `Post-switch`, data=d_all, 
#             family = "binomial"))
# 
# summary(glm(SI_implicature ~ `Post-switch` + GQ_some_correct + test_age, data=d_all, 
#             family = "binomial"))
# summary(glm(SI_implicature ~ `Post-switch` + GQ_some_correct + test_age, data=d_all, 
#             family = "binomial"))
# summary(glm(SI_implicature ~  `Post-switch` + GQ_some_correct, data=d_all, 
#             family = "binomial"))
# summary(glm(SI_implicature ~  GQ_some_correct + test_age, data=d_all, 
#             family = "binomial"))
# 
# summary(glm(SI_none ~ `Post-switch` + GQ_none_correct + test_age, data=d_all, 
#             family = "binomial"))
# summary(glm(SI_none ~ `Post-switch` + GQ_none_correct, data=d_all, 
#             family = "binomial"))
# summary(glm(SI_none ~ GQ_none_correct + test_age, data=d_all, 
#             family = "binomial"))
# 
# summary(glm(SI_implicature ~ `Post-switch` + test_age, data=d_all, 
#             family = "binomial"))
# summary(glm(GQ_none_correct == 0 ~  DCCS_post, data=d_all, 
#             family = "binomial"))
# summary(glm(GQ_none_correct == 0 ~  DCCS_post + test_age, data=d_all, 
#             family = "binomial"))
```
